A methodology for calculating active source-time functions from broadband piezoelectric sensors in the laboratory

### 2020-04-29 Article_file_Source_reconstruction.tex
Updates from Overleaf

\begin{equation}
\label{eq1}
           u_{k}\left( \mathbf{x}, t \right)  =  
            f_{j}\left( \mathbf{\xi}, \tau \right) \ast 
            g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right).
\end{equation}
\noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$. For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties. The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ or the identity convolution.

Piezoelectric transducers measure a voltage caused by the compression of the lead zirconate titanate (PZT) crystal in the surface normal direction $s\left( \mathbf{x}, t \right)$. We can relate the true surface displacement $u_{k}$ to voltage measurement $s$ using the instrument response, which is given as
   \begin{equation}
    \label{eq2}
        s\left( \mathbf{x}, t \right) =
            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(\mathbf{x},t \right).
    \end{equation}
    \noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the forces which produced them:

@@

\noindent where $A_{0}$ = 1 N for the normalized case, $\Gamma$ and $\Lambda$ are the decay and vibration parameters of the normalized force-time function. We note that the subscript $_{j}$ has disappears since we are assuming that the normalized force is acting only in the $`3'$-direction. Later, we will describe how these two parameters are used in an inversion to minimize the errors between the theoretical displacements $u_{k}$ and measured signals $s$ over all the measured sensors. For the case in Figure \ref{fig2b}(d), $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, which represented the best-fit solution for our analysis of the specific PZT used in this study following the excitation pulse in Figure \ref{fig1}(d).

@@

\begin{equation}
    \label{eq5}
        I_{k}\left(\omega \right) = 
        S\left( \mathbf{x}, \omega \right) \cdot \left[ F_{j}\left( \mathbf{\xi}, \hat{\omega} \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega} \right)\right]^{-1} .
\end{equation}

@@

For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu2020} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm. The balls had elastic modulii of $E_{ball}$ = 210 GPa and Poisson ratio of $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}. Once the force-time function is know, we use equation \eqref{eq5}, now with $F_{ball}\left( \mathbf{\xi}, \hat{\omega} \right)$, which represents the Fourier transform of the ball drop, to calculate the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.  Calculating the lower frequency instrument response (i.e. 1 kHz to 50 kHz ) is not straightforward and the readers should also consult \citet{Wu2018} for a summary of methods. Figure \ref{fig6}(a) shows the full instrument response for all the passive sensors shown in Figure \ref{fig1}(b). The color coding related to the sensors epicentral distance from the ball drop source. In this study, we are only interested in the higher frequency (100 kHz to 1 MHz) sensor behavior for the reconstruction of the PZT actuator force time function. This range is shown in Figure \ref{fig6}(b). We see that the instrument response is insensitive to the take-off angle. This is important to the analysis and will be addressed in the more detail later. This insensitivity has also been acknowledged in the past for the same KRNPC-BB conical-style sensors used here \citep{Goodfellow2015, Selvadurai2019}.  Results from this calibration campaign are summarized and more details have been given in \citet{Wu2020}.

@@

\subsection{Spectral Deconvolution of the Problem}

Having the specific broadband instrument response, solved using the well-understood ball drop source for our exact sensor-source layout, is paramount to accurately model the force-time function of the PZT actuator described by equation \eqref{eq4b}.   If we now consider the original problem in Figure \ref{fig2}, we can start with the recorded signal produced from the PZT actuator and use the instrument response to determined the mechanical vibration.  In the Fourier domain, we can rearrange the left hand side of equation \eqref{eq3} to estimate the spectral response of the theoretical vibration $U_{k}(\mathbf{x},t)$ caused by the transient PZT actuator:

@@

Approaching the problem from the source side (right hand side of equation \eqref{eq3}), we can also estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is shown as:

\begin{equation}
    \label{eq6a}
\begin{split}
U_{k}\left( \mathbf{x}, \omega \right) & = 
       F_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right).
\end{split}
\end{equation}

@@

\begin{equation}
    \label{eq6b}
\begin{split}
U_{k}\left( \mathbf{x}, \omega \right) & = 
       A_{0}\cdot \delta (\omega)\cdot F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right),
\end{split}
\end{equation}

\noindent where the Fourier transform of the scaling parameter is $\mathcal{F}[A_{0}] = A_{0}\cdot\delta(\omega)$ and $\delta$ is the Dirac delta function.  Next we can combine equations \eqref{eq6} and \eqref{eq6b} to solve for the scaling factor for the force-time function $A_{0}$:

\begin{equation}
    \label{eq6b}
\begin{split}
A_{0} = \mathcal{F} ^{-1}[A_{0}\cdot \delta (\omega)] & = \frac{S\left( \mathbf{x}, \omega \right) } 
{ I_{k}\left( \mathbf{x},\omega \right)\cdot F^{*}_{j}\left( \mathbf{\xi}, \hat{\omega} \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \hat{\omega}\right)},
\end{split}
\end{equation}

\noindent where $\mathcal{F}^{-1}[\cdot]$  is the inverse Fourier transform. We see that all of the components on the right hand side can be measured ($S$) or calculated ($G_{kj}$) or have been determined \textit{a priori} ($I_{k}$) . We must assume that $A_{0}$ is constant over time and and the force-time function $f(\mathbf{\xi}, \tau)$, in equation \eqref{eq4b}, accurately captures the force released during the impulsive excitation of the PZT actuator.

\section{Results}
\label{results}

In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b).  Waveforms have been color coded following Figure \ref{fig1}(b) to show measurements taken at similar epicentral distances. These waveform we produced by actively exciting the source sensor located at the top central location of the steel platen. For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen.  This allows us to analyze the wave using the approximation that the plate is in fact semi-infinite. Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.  Figure \ref{fig3}(b) shows the Green's functions (EGF) at a give epicentral location from the source. We call this the empirical Green's function since it is a numerical approximation of the true Green's function that is the resulting ground displacements $u$ at point $\mathbf{x}$ from a unit impulse function $\delta_{j}(\mathbf{\xi}, \tau)$. In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) for the numerical models.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG3.pdf} 
\caption{\textbf{(a)} Measurements the array of passive PZT transducers from a PZT actuator source described in Figure \ref{fig1}(d). The color scheme represents the different epicentral locations of each sensor in Figure \ref{fig1}(b).  \textbf{(b)} Green's function solutions using generalized ray theory for a semi-infinite elastic, homogeneous steel plate at different epicentral locations.  The empirical Green's function (EGF) is the numerical estimate of the true Green's function, which is displacements produced from the unit impulse force $\delta_{j}(\mathbf{\xi}, \tau)$. We see the various phase arrival predicted from the model.}
	\label{fig3} 
\end{figure}

Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.  For clarity, we only show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) from the epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively. We see that the sensors appear to capture the multiple phase arrivals and this is believed to be due to the conical nature of the PZT crystal and its ability to capture wave arrivals at high azimuthal incident angles \citep{Selvadurai2019}. Results in Figure \ref{fig4} are representative of the measurements across all 13 passive sensors.

@@

To best show the approach we take to solve for the force time function produced by the active source, we focus on the measurements taken from sensors A3 at epicentral distance $x$ = 46 mm. Figure \ref{fig5}(a) shows the measurements and EGFs.  We focus on detail B, which looks at the first arrival P wave.  In Figure \ref{fig5}(b) this is shown in more detail with the sensors (green trace) and EGF (black trace) clearly visible.  Since we know that, in the time domain, the signal produced on the sensors the force-time function are convolved with the associated Green's function, the shape of the specific wave with be representative of the source. The blue curve in Figure \ref{fig5}(b) is a best-guess approximation of the source and will be use to estimate the general normalized force-time function $f^{*}_{j}$ from equation \eqref{eq4}.

@@

 We created the normalized force-time function based on characteristic of the first arrival P wave.  In Figure \ref{fig5}(c) we show the methodology for generating $f^{*}_{j}$.  We based this on the technical specifications of the high-voltage pulsing unit described in Section \ref{XXX}. In this experiment we applied a 100V pulse, which translates into a positive pulse, followed by a delay, then a negative pulse.  We approximated this behavior using piecewise discontinuous step functions (red curve) that was convolved with a 0.6 $\mu$s triangle function to smoothen the step function. This produced the blue curve which matched the general shape of the P wave arrival in Figure \ref{fig5}(c).  We will use this as a forward model to approximate the source-time from the active PZT source. We clearly see that the normalized force-time function varies from [-1,1], which is appropriate for our definition of $f^{*}$ in Section \ref{XXX}.

To solve for the scaling function $K(\hat{\omega})$ we need to know the instrument response function $i(t)$. For this study, we use the results from \citet{Wu2020}. They performed multiple ball drops to create known force-time functions at the same location as the active sensors. The same sensors were used in their study and a series of different ball sizes where used (diameters = 0.3 mm, .....to 1.5 mm).  \citet{Wu2020} modeled long times to also capture how the sensors responded to frequencies as low as $f$ =1 kHz, following the methodology by \citet{Wu2018}.  Figure \ref{fig6}(a) shows the full instrument response function for each sensor in the Fourier domain (see equation \ref{eq5}).  Figure \ref{fig6}(b) focuses only on the results for frequencies between $f$ = 100 kHz to 1000 kHz, which is more important to our understanding of the true force-time function in our case.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG7.pdf} 
\caption{\textbf{(a)}  }
	\label{fig7} 
\end{figure}

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG8.pdf} 
\caption{\textbf{(a)}  }
	\label{fig8} 
\end{figure}

@@

>>>>

\begin{equation}
\label{eq1}
           u_{k}\left( \mathbf{x}, t \right)  =  
            f_{j}\left( \mathbf{\xi}, \tau \right) \ast 
            g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right).
\end{equation}

\noindent We note that $\ast$ represents convolution in the time domain, $f$ is the force acting in the $j$ direction at location $\mathbf{\xi}$ and $g_{kj}\left( \mathbf{x}, t;\mathbf{\xi}, \tau \right)$ is the elastodynamic Green's function describing the displacement $u$ in the direction $k$ at location $\mathbf{x}$. For the elastodynamic solutions studied here, we assume that convolution $\ast$ is applicable since the system in question are linear time-invariant (LTI) and that convolution has commutativity, associative and distributive properties. The true Green's function is the displacement field for the unit impulse force $\delta_{j}$ or the identity convolution.

Piezoelectric transducers measure a voltage caused by the compression of the lead zirconate titanate (PZT) crystal in the surface normal direction $s\left( \mathbf{x}, t \right)$. We can relate the true surface displacement $u_{k}$ to voltage measurement $s$ using the instrument response, which is given as
   \begin{equation}
    \label{eq2}
        s\left( \mathbf{x}, t \right) =
            u_{k}\left( \mathbf{x}, t \right) \ast i_{k}\left(\mathbf{x},t \right).
    \end{equation}

    \noindent Combining \eqref{eq1} and \eqref{eq2}, we can represent the measured voltage to the forces which produced them:

@@

\noindent where $A_{0}$ is the scaling factor (= 1 N for the normalized case), $\Gamma$ and $\Lambda$ are the decay and vibration parameters of the normalized force-time function. We note that the subscript $_{j}$ has disappears since we are assuming that the normalized force is acting only in the $`3'$-direction. Later, we will describe how these two parameters are used in an inversion to minimize the errors between the theoretical displacements $u_{k}$ and measured signals $s$ over all the measured sensors. For the case in Figure \ref{fig2b}(d), $\Gamma$ = 0.7 MHz and $\Lambda$ = 4.7 MHz, which represented the best-fit solution for our analysis of the specific PZT used in this study following the excitation pulse in Figure \ref{fig1}(d).

@@

\begin{equation}
    \label{eq5}
        I_{k}\left(\omega \right) = 
        S\left( \mathbf{x}, \omega \right) \cdot \left[ F_{j}\left( \mathbf{\xi}, \omega \right) \cdot G_{kj}\left( \mathbf{x}, \omega; \mathbf{\xi}, \omega \right)\right]^{-1} .
\end{equation}

@@

For the identical configuration of sensors shown in Figure \ref{fig1}(b), \citet{Wu2020} has dropped a range of small stainless steel (404) balls with diameters ranging from $d_{ball}$ = 0.3, 0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 1.0, 1.5, 2.0 and 2.5 mm. The balls had elastic modulii $E_{ball}$ = 210 GPa and Poisson ratio $\nu_{ball}$ = 0.303, which allow them to calcaute the specific force-time function from Hertzian contact theory \citep[see also e.g.][]{McLaskey2010, McLaskey2012}. Once the force-time function is know, we use equation \eqref{eq5}, now with $F_{ball}\left( \mathbf{\xi}, \omega \right)$, which represents the Fourier transform of the ball drop, to calculate the broadband instrument response $I_{k}(\omega)$ from 1 kHz to 1 MHz.  Calculating the lower frequency instrument response (i.e. 1 kHz to 50 kHz ) is not straightforward and the readers should also consult \citet{Wu2018} for a summary of methods. Figure \ref{fig6}(a) shows the full instrument response for all the passive sensors shown in Figure \ref{fig1}(b). The color coding related to the sensors epicentral distance from the ball drop source. In this study, we are only interested in the higher frequency (100 kHz to 1 MHz) sensor behavior for the reconstruction of the PZT actuator force time function. This range is shown in Figure \ref{fig6}(b). We see that the instrument response is insensitive to the take-off angle. This is important to the analysis and will be addressed in the more detail later. This insensitivity has also been acknowledged in the past for the same KRNPC-BB conical-style sensors used here \citep{Goodfellow2015, Selvadurai2019}.  Results from this calibration campaign are summarized and more details have been given in \citet{Wu2020}.

@@

\subsection{Spectral Deconvolution of the Problem}
\label{Spec_deconv}
Having the specific broadband instrument response, solved using the well-understood ball drop source for our exact sensor-source layout, is paramount to accurately model the force-time function of the PZT actuator described by equation \eqref{eq4b}.   If we now consider the original problem in Figure \ref{fig2}, we can start with the recorded signal produced from the PZT actuator and use the instrument response to determined the mechanical vibration.  In the Fourier domain, we can rearrange the left hand side of equation \eqref{eq3} to estimate the spectral response of the theoretical vibration $U_{k}(\mathbf{x},t)$ caused by the transient PZT actuator:

@@

Approaching the problem from the source side (right hand side of equation \eqref{eq3}), we can estimate the mechanical vibration caused by the force of the PZT actuator convolved with the Green's function solution, which in the Fourier domain is shown as:

\begin{equation}
    \label{eq6a}
\begin{split}
U_{k}\left( \mathbf{x}, \omega \right) & = 
       F_{j}\left( \mathbf{\xi}, \omega \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \omega\right).
\end{split}
\end{equation}

@@

\begin{equation}
    \label{eq6b}
\begin{split}
U_{k}\left( \mathbf{x}, \omega \right) & = 
       A_{0}\cdot \delta (\omega)\cdot F^{*}_{j}\left( \mathbf{\xi}, \omega \right)  \cdot G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \omega\right),
\end{split}
\end{equation}

\noindent where the Fourier transform of the force-time magnitude parameter is $\mathcal{F}[A_{0}] = A_{0}\cdot\delta(\omega)$ and $\delta$ is the Dirac delta function.  Next we can combine equations \eqref{eq6} and \eqref{eq6b} to solve for the scaling factor for the force-time function $A_{0}$:

\begin{equation}
    \label{eq6c}
\begin{split}
 F_{j}\left( \mathbf{\xi}, \omega \right) = A_{0}\cdot \delta (\omega)  \cdot F^{*}_{j}\left( \mathbf{\xi}, \omega \right) & 
=\left[ \frac{S\left( \mathbf{x}, \omega \right) } 
{ I_{k}\left( \mathbf{x},\omega \right)} \right]
\left[ \frac{1}{ G_{kj}\left(  \mathbf{x}, \omega; \mathbf{\xi}, \omega\right)} \right].
\end{split}
\end{equation}

\noindent We see that all of the components on the right hand side can be measured ($S$), can be calculated ($G_{kj}$) or have been determined \textit{a priori} ($I_{k}$) . In this approach we assume that $A_{0}$ is constant over time and and the force-time function $f(\mathbf{\xi}, \tau)$ described accurately by equation \eqref{eq4b}.

\section{Results}
\label{results}
\subsection{Time domain analysis}
A total of 1000 pulses of the PZT actuator were performed but for our results we show a single pulse to show the methodology that follows equations \eqref{eq1} to \eqref{eq6b}.  The source was highly repeatable in at the high-frequencies we investigated.  From the 1000 tests, the average  Pearson correlation coefficient from the stacked mean was $R$ = \textbf{0.95}. In Figure \ref{fig3}(a) we show measurements on all passive sensors PZT sensors depicted in Figure \ref{fig1}(b) for a random pulse with color indicating different epicentral distances. For our analysis, we only the first 50 $\mu$s of signal since we do not want to pollute the data with reflections from the boundary of the platen that would occur if longer signals were analyzed. The sampling rate was $F_{s}$ = 20 MHz making each trace 1000 samples. Since boundary reflections are not considered, we can approximate that the plate is in fact semi-infinite. Under this assumption we are able to solve for the Green's functions using the generalized ray theory code provided by \citet{Hsu1985} and modified for MATLAB by \citet{McLaskey2012}.  Figure \ref{fig3}(b) shows the Green's functions at different epicentral locations, moving out from the source at $x$ = 0 mm. We call these approximations the empirical Green's function (EGF) since it is a numerical approximation of the true Green's function.  The true Green's function can be calculated by replacing the force-time function in equatoin \eqref{eq1} with the a unit impulse (Dirac delta) function $\delta_{j}(\mathbf{\xi}, \tau)$. In Figure \ref{fig3}(b) we also show the wave phase arrivals (P, S, PPP, PPPPP) from the numerical models.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1.0]{FIG3.pdf} 
\caption{\textbf{(a)} Measurements taken from the passive PZT transducers from a single transient PZT excitation described in Figure \ref{fig1}(d). The color scheme represents the different epicentral locations of each sensor in Figure \ref{fig1}(b).  \textbf{(b)} Green's function solutions determined using generalized ray theory for a semi-infinite elastic, homogeneous steel plate at different epicentral locations.  We see the various phase arrival predicted from the model.}
	\label{fig3} 
\end{figure}

Figure \ref{fig4} compares the theoretical Green's function $g_{kj}$ to the measured signals $s$.  For clarity, we only show the sensors A1 (red), A2 (yellow), A3 (green) and A4 (blue) at epicentral distances of 0 mm, 23 mm, 46 mm and 69 mm, respectively. We see that the sensors captures various phase arrivals predicted form the model. The ability of these sensors to accurately capture wave arrivals and information even at high azimuthal incident angles has been discussed in the literature \citep{Goodfellow2015, Selvadurai2019} and is due to the conical geometry of the PZT crystal.

@@

We further focus on the measurements taken from sensors A3 at epicentral distance $x$ = 46 mm. Figure \ref{fig5}(a) shows the measurements (green) and EGF (black line).  Detail B in Figure \ref{fig5}(b) focuses on the first arrival P wave. As discussed in Section \ref{force_time}, the measured waveforms will display features of the source due to the convolution operations in equations \eqref{eq1} to \eqref{eq3}. In Detail B we superimpose the normalized force-time function $f^{*}$ from Figure \ref{fig2b}(d) for reference. We see that there appears to be some similarities in our measured signals that would justify our hypothesized force-time function given in equation \eqref{eq4b}.  While the fit is not perfect -- the signal sensor A3 appears to a lower decay parameter $\Gamma$ -- this will be addressed when we simultaneously invert to match these variables on all sensors. Before doing so, we must calculate the scaling factor in the frequency domain using equation \eqref{eq6c}.

@@

\subsection{Frequency domain analysis}
In this section we perform the discrete Fourier transform of the measured and theoretical traces in Figure \ref{fig3}.  For clarity we only show the results from the sensor A3 shown in Figure \ref{fig5} to illustrate the steps taken to solve for the scaling function $A_{0}$. To minimize the uncertainty that can occur from non-uniform spacing of samples of the Fourier frequencies linear scale, we average over multiple bins while evenly spacing our samples on the logarithmic scale.  We re-sample all DFT on the with 41 samples from 100 kHz to 1000 kHz.  While this might cause some averaging uncertainties between neighboring frequencies, this does not affect our final estimates of the scaling factor  $A_{0}$ in equation \eqref{eq4c} since, as we will see, we take estimate the scaling factor $A_{0}$ as a single average over the full range of frequencies.

Figure \ref{fig7}(a) shows the Fourier transform of the signal ($\mathcal{F}[s] = S$, green line) and instrument response ($\mathcal{F}[i] = I_{k}$, black line) for sensor A3 between frequencies from 100 kHz to 1000 kHz. Figure \ref{fig7}(b) shows spectral estimates of the theoretical ground motions $S$ from the signal side, i.e. from equation \eqref{eq6}.  As discussed in Section \label{Spec_deconv}, we can also try to estimate  theoretical ground motions from the source side.  Figure \ref{fig7}(c) shows the DFT of the empirical Green's function ($\mathcal{F}[g_{kj}] = G_{kj}$, black line) and the normalized force-time function ($\mathcal{F}[f^{*}_{j}] = F^{*}_{j}$, blue line). Figure \ref{fig7}(d), shows the spectral estimates of $F_{j}$ determined from using the previous results with equation \eqref{eq6c}.  The spectral response is relatively flat with a mean value of 3.4 N/Hz for our analysis on sensor A3.  Using the same approach on all other passive sensors we see an average 3.3 N/Hz with a standard deviation of 0.66 N/Hz.

\begin{figure}[ht]
     	\centering
\includegraphics[scale= 1]{FIG7.pdf} 
\caption{\textbf{(a)} Discrete Fourier transform (DFT) of the measured waveform $S$ (green line) and the instrument response from sensor $I_{k}$ (black line) at A3 between 100 kHz to 1000 kHz. \textbf{(b)} Spectral estimates of the ground displacements $U_{k}$ (gray line) obtained from spectral division using equation \eqref{eq6}. \textbf{(c)} We show the DFT of the normalized force-time function $F_{j}^{*}$ (blue line) and the empirical Green's function $G_{kj}$ (black line) . \textbf{(d)} Spectral estimates of the corrected force time function $F$ calculated from the spectral estimates of the signal, instrument response, Green's function, normalized force time function. The spectral mean from between 100 kHz to 1000 kHz is shown.}
	\label{fig7} 
\end{figure}

Using the calculations highlighted in Figure \ref{fig7}, we use the inverse Discrete Fourier transform (IDFT) to return the force-time function into the time domain. Firstly, due to the fact that the frequency response is relatively flat over the 100 kHz to 1000 kHz range (Figure \ref{fig7}(d)) we use the mean spectral value to scale the spectrum of normalized force-time function $F^{*}$ (blue line in Figure \ref{fig7}(c)) prior to performing the IDFT. We choose to scale the normalized source time function since, due to properties of the IDFT, we require frequencies outside the range we are able to estimate the spectral calculations shown in Figure \ref{fig7}.  We note that lower frequencies cannot be studied due to the plate finite geometry that limits our analysis of the signal to 50 $\mu s$.  In Figure \ref{fig9}(a) we show the broadband DFT of the normalized force-time function (blue line).  We scale this with the scaling factor from Figure \ref{fig7}(d) to obtain the re-scaled force-time function in the Fourier domain $F$ (black line). We have also applied a 4-pole bandpass butterworth filter (red line) between 100 kHz and 1000 kHz, which will be used in our time domain comparison between synthetic estimates to the filtered and unfiltered signals. Figure \ref{fig9}(b) shows the IDFT to our estimates of the normalized (blue), unfiltered (black) and filtered (red) signals.  The corrected force-time function in the time domain estimates that the peak force of $\sim$ 3.4 N. This estimate fall within a reasonable range of estimated force-time function for conical sensor estimate by \citet{Breckenridge1990} $\sim $ 1.2 N for a transient step function over 1 $\mu s$ with an amplitude of 100 V. We note that if the systems studied by \citet{Breckenridge1990} was linear, for a 200 V we would expect a 2.4 N step.  While there are discrepancies, the exact details of the conical PZT (geometry, casing, backing mass, damping material, etc.) are not given so it is difficult to perfectly characterize the discrepancies. Moreover, the voltage-time function that excited the PZT actuator differs in each study; we employ a pulse-discharge excitation, whereas they employed a step-hold.

@@

\subsection{Synthetic reconstructing}
